%Type setting your answer here.

\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks = true,
        linkcolor = blue,
        urlcolor  = blue,
        citecolor = blue,
        anchorcolor = blue]{hyperref}

\newcounter{question}
\newenvironment{question}[1][]{\refstepcounter{question}\par\medskip
\noindent\textbf{\thequestion. #1} \rmfamily\begin{bfseries}}{\end{bfseries}\medskip}

\newcounter{subquestion}[question]
\newenvironment{subquestion}[1][]{\refstepcounter{subquestion}\par\medskip
\noindent\textbf{\thequestion.\thesubquestion #1} \rmfamily\begin{bfseries}}{\end{bfseries}\medskip}

\title{CSC 565 2020 Fall Homework 4}
%replace name and unityID for all group members.
\author{
name1, unityID1 \\
\and
name2, unityID2
}

\begin{document}

\maketitle

\noindent You can create a latex project of this homework through this \href{https://www.overleaf.com/docs?snip_uri=https://donsheehy.github.io/graphtheoryhomework/hw4.tex}{link}.

\section*{Simplicial Maps and Contractions}

\begin{question}
    Give a contraction $C_5$ to $C_3$.
\end{question}
\\\\
\textit{Answer:}
\\\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Type setting your answer here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{question}
    Give a surjective simplicial map $C_5$ to $C_3$ that is \emph{not} a contraction.
\end{question}
\\\\
\textit{Answer:}
\\\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Type setting your answer here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Contracting Edges in Planar Graphs}
\begin{question}
    Let $G$ be a planar graph with $n$ vertices, $m$ edges, and $f$ faces.
    Let $e\in E_G$ be an edge of $G$.
    How many vertices, edges, and faces can $G' = G/e$ have?  This is the graph $G$ with the edge $e$ contracted.
    Please give your answer as a collection of $(n',m',f')$ triples.
\end{question}
\\\\
\textit{Answer:}
\\\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Type setting your answer here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Forbidden Minors}
\begin{question}
    Let $H_0,\ldots, H_{k-1}$ be a set of graphs.
    Let $S$ be the set of graphs $G$ such that for all $i\in [k]$,
    \[
      H_i \not\preceq_M G.
    \]
    Let $G\in S$ and let $G'$ be a minor of $G$.
    Prove that $G'\in S$.
\end{question}
\\\\
\textit{Answer:}
\\\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Typeset your answer here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newpage
\section*{Planar $3$-connected graphs}
\begin{question}
  Let $G$ be a planar $3$-connected graph.
  Let $H = G + e$ still be a planar graph where $e$ is an edge.
  Show that $H^*$ contracts to $G^*$. Note that $H^*$ is the dual of $H$.
\end{question}
\\\\
\textit{Answer:}
\\\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Typeset your answer here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
